---
title: ""
author: "Irene Rodríguez"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_book:
    citation_package: biblatex
    use-biblatex: true
    toc: false
    number_sections: false
    latex_engine: lualatex
header-includes:
  - \usepackage{titling}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[nottoc, numbib]{tocbibind}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
bibliography: ["Literature/bibliography.bib"]
link-citations: true
biblio-style: apa
colorlinks: citecolor
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE, fig.pos = 'H')
```

```{r library}
library(expss) #import SPSS data sets
library(naniar) #turn into NA
library(tidyverse)
library(zoo) #manage Dates
library(sjlabelled) #label values in variables
library(stargazer) #build regression tables
library(ggeffects) #build plots of predicted values
library(ggthemes) #change plot themes (not default ggplot themes)
library(gmodels) #crosstables
```


\begin{titlepage}
\begin{center}
\vspace*{2\baselineskip}
\LARGE{\textbf{The dangers of legitimation:} \\How the presence of RRPs in Parliament can increase anti-immigration attitudes}\\
\vspace*{1\baselineskip}
\small{By}\\
\Large{\textbf{Irene Rodríguez, PhD Candidate}}\footnote{\textbf{Affiliation:} Universitat Pompeu Fabra}\footnote{\textbf{Contact:} \href{mailto:irene.rodriguez@upf.edu}{irene.rodriguez@upf.edu}}
\end{center}
\vspace*{5\baselineskip}
The author has no conflicts of interest to dislose, nor has she received funding for the elaboration of this article.\\
Raw data for this article can be found at \href{https://www.cis.es/cis/opencm/ES/11_barometros/index.jsp}{Centro de Investigaciones Sociológicas}, and processed data for the analysis can be found on \href{https://github.com/irenerodriguezlopez/Legitimation.git}{GitHub}.
\end{titlepage}